Next Trippy Structures\thanks{Supported by organization x.}

### 2019-01-08 paper.tex
Example figures (beta)

@@

@@

\section{Proposed Structures}
As of today, we are not aware of any indexing structure that would allow to efficiently represent trajectories that could also support all the kinds of queries described in Section~\ref{seq:rq}. For this reason, we propose two data structures, \acumm and \ctr. The first is targeted for queries of type A, solving most aggregation queries in constant time, while the later can be used for queries of type B.

@@

\subsection{\ctr}
A user trip can be represented by the stops where the user gets on the transportation system, so from now on we will consider a trip as a sequence of triplets $<s,l,j>$, where $s$, $l$ are, respectively, stop and line identifiers, while $j$ are the journey codes corresponding to the journeys that compose the trip. Additionally, as we are interested in knowing where the trips end, we also represent the last stop where the user got off, which line and journey will logically match the line and journey of the last get-on stop. Although it is generally hard to obtain information about the last destination stop of a trip, many transportation companies are investing effort in providing it, either by implementing systems to keep track of users as they leave their system or estimating it based on previous trips made by that user\marginnote{[CITATION NEEDED]}.

@@

>>>>

\subsection{Our previous works in trip representation}
So we speak about IS and SPIRE 2018 version here.

@@

\begin{figure}
\includegraphics[width=\textwidth]{example_network.eps}
\caption{An example network for our model, with two lines and five stops}
\label{fig:example_network}
\end{figure}

@@

\section{Proposed Structures}
As of today, we are not aware of any indexing structure that would allow to efficiently represent trajectories that could also support all the kinds of queries described in Section~\ref{seq:rq}. For this reason, we propose two data structures, \acumm~and~\ctr. The first is targeted for queries of type A, solving most aggregation queries in constant time, while the later can be used for queries of type B.

@@

\subsection{\ctr}
A user trip can be represented by the stops from the transportation system boarded by a user, so from now on we will consider a trip as a sequence of triplets $<s,l,j>$, where $s$, $l$ are, respectively, stop and line identifiers, while $j$ are the journey codes corresponding to the journeys that compose the trip. Additionally, as we are interested in knowing where the trips end, we also represent the last stop where the user has alighted, which line and journey will logically match the line and journey of the last boarding stop. Although it is generally hard to obtain information about the last destination stop of a trip, many transportation companies are investing effort in providing it, either by implementing systems to keep track of users as they leave their system or estimating it based on previous trips made by that user\marginnote{[CITATION NEEDED]}.

@@

\begin{figure}
\includegraphics[width=\textwidth]{example_trips.eps}
\caption{An example of five trips represented on \ctr~(WIP)}
\label{fig:example_ctr}
\end{figure}
